---
title: "UZIMA Fabric Data Access"
output: html_document
---

# Sign In And Read Data

Use this file from your personal computer after your account has been approved for Fabric access.

Run the sections from top to bottom. When Microsoft asks you to sign in, use your approved email address.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = FALSE)
```

# 1. Connect

This uses Microsoft sign-in. To use Fitbit or Qualtrics, change only `Database=uzima_db_backup` in the connection string.

```{r connect}
if (!requireNamespace("DBI", quietly = TRUE)) install.packages("DBI")
if (!requireNamespace("odbc", quietly = TRUE)) install.packages("odbc")

connection_string <- paste0(
  "Driver={ODBC Driver 18 for SQL Server};",
  "Server=fis5jjpzajqe5fxqs4z3vlsjde-zgopmz6jacoezkc3hd6da52lpm.datawarehouse.fabric.microsoft.com;",
  "Database=uzima_db_backup;",
  "Authentication=ActiveDirectoryInteractive;",
  "Encrypt=yes;",
  "TrustServerCertificate=no;"
)

con <- DBI::dbConnect(odbc::odbc(), .connection_string = connection_string)
```

# 2. See Available Tables

This shows the tables or views you are allowed to read.

```{r list-tables}
tables <- DBI::dbGetQuery(con, "
  SELECT TABLE_SCHEMA, TABLE_NAME
  FROM INFORMATION_SCHEMA.TABLES
  ORDER BY TABLE_SCHEMA, TABLE_NAME
")

head(tables, 30)
```

# 3. Read A Small Sample

After you see the table list, change `table_to_read` to the approved table or masked view you need.

```{r read-sample}
table_to_read <- "dbo.dimenrolledparticipants"

sample_data <- DBI::dbGetQuery(con, paste("SELECT TOP 10 * FROM", table_to_read))
sample_data
```

# 4. Close The Connection

```{r disconnect}
DBI::dbDisconnect(con)
```