---
title: "UZIMA Fabric Data Access"
output: html_document
---

# Read Data Through Key Vault And cdiofabric

This example reads the ODBC connection string from Key Vault.

The connection string uses the `cdiofabric` managed identity to connect to Fabric. It must not use browser or email sign-in.

Run this from an Azure resource that has the `cdiofabric` user-assigned managed identity attached.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = FALSE)
```

# 1. Connect

```{r connect}
if (!requireNamespace("AzureKeyVault", quietly = TRUE)) install.packages("AzureKeyVault")
if (!requireNamespace("DBI", quietly = TRUE)) install.packages("DBI")
if (!requireNamespace("odbc", quietly = TRUE)) install.packages("odbc")

# Change only this value when you need another database.
# Options: "uzima_db_backup", "HCW_fitbit_data", "Qualtrics"
database_name <- "uzima_db_backup"
managed_identity_client_id <- "4ae6ed7b-b72c-4853-9a3c-10699e60f63e"

vault <- AzureKeyVault::key_vault(
  "uzima-fabric-tokens",
  as_managed_identity = TRUE,
  token_args = list(client_id = managed_identity_client_id)
)

connection_string <- vault$secrets$get("fabric-odbc-connection-string")$value

if (grepl("Interactive", connection_string, fixed = TRUE)) {
  stop("Key Vault ODBC secret must use managed identity auth, not browser or email sign-in.")
}

if (!grepl("Authentication=ActiveDirectoryMsi", connection_string, fixed = TRUE)) {
  stop("Key Vault ODBC secret is missing Authentication=ActiveDirectoryMsi.")
}

connection_string <- sub("DATABASE=[^;]+;", paste0("DATABASE=", database_name, ";"), connection_string)

con <- DBI::dbConnect(odbc::odbc(), .connection_string = connection_string)
```

# 2. See Available Tables

```{r list-tables}
tables <- DBI::dbGetQuery(con, "
  SELECT TABLE_SCHEMA, TABLE_NAME
  FROM INFORMATION_SCHEMA.TABLES
  ORDER BY TABLE_SCHEMA, TABLE_NAME
")

head(tables, 30)
```

# 3. Read A Small Sample

Change `table_to_read` to the approved table or masked view you need.

```{r read-sample}
table_to_read <- "dbo.dimenrolledparticipants"

sample_data <- DBI::dbGetQuery(con, paste("SELECT TOP 10 * FROM", table_to_read))
sample_data
```

# 4. Combine Two Approved Tables

Use this only when `cdiofabric` has access to both approved tables or masked views.

```{r combine-data, eval=FALSE}
merge_question <- "
SELECT TOP 100
  p.Gender,
  p.Age,
  f.date,
  f.steps
FROM uzima_db_backup.dbo.dimenrolledparticipants p
JOIN HCW_fitbit_data.dbo.fitbitdailydata f
  ON p.ParticipantIdentifier = f.participantidentifier
"

merged_data <- DBI::dbGetQuery(con, merge_question)
merged_data
```

# 5. Close The Connection

```{r disconnect}
DBI::dbDisconnect(con)
```